\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-26 paper/experiments.tex
paper: removed planning times, just left in text, added todo for table of SMAPE

\Cref{fig:plantimes} provides a summary of the planning times for each of the queries.
We exclude the planning time for queries that impute at base table, as that requires no
planning. In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime by \ProjectName{}. The one-standard-deviation
intervals around the mean planning time often overlap, suggesting the planning component is
constant in $\alpha$.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
\caption{Planning times for each query}
\label{fig:plantimes}
\end{figure}

@@

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Values of $0.0$,
    $100.0$, or $NaN$ indicate uninformative values.} %TODO MJS
\label{table:smape}
\end{table}

>>>>

%\Cref{fig:plantimes} provides a summary of the planning times for each of the queries.
%We exclude the planning time for queries that impute at base table, as that requires no
%planning.

In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime. In all cases, the optimizer
returned a query plan within 40ms, with times roughly constant between levels of $\alpha$.

% The one-standard-deviation
%intervals around the mean planning time often overlap, suggesting the planning component is
%constant in $\alpha$.

%\begin{figure}
%\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
%\caption{Planning times for each query}
%\label{fig:plantimes}
%\end{figure}

@@

\begin{table}
\todo{Consider switching to graph, or changing table layout..not very intuitive right now.}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Values of $0.0$,
    $100.0$, or $NaN$ indicate uninformative values.} %TODO MJS
\label{table:smape}
\end{table}
